### 2016-01-16 paper.tex
Mention blockage ratio and why it was not corrected for; resolves #36

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed precise control
of the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted at a fixed distance from the servo motor
via a moment arm provided a redundant torque measurement. Turbine shaft angle
was measured using the servo drive's emulated encoder output, set to $10^5$
counts per turbine shaft revolution. Carriage speed, and therefore inflow
velocity was measured using a linear encoder with 10 $\mu$m resolution. All of
these performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed turbine
angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

@@

>>>>

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The blockage ratio based on the rotor
frontal and tank cross-sectional area was 10\%. The turbine was mounted in a
frame built from NACA 0020 struts, attached to the tow carriage by four linear
bearings, which transfer all streamwise force to a pair of S-beam load cells.
The turbine shaft RPM was controlled by a servo motor system, which allowed
precise control of the turbine tip speed ratio. The load torque was measured by
an inline rotary torque transducer. A load cell mounted at a fixed distance from
the servo motor via a moment arm provided a redundant torque measurement.
Turbine shaft angle was measured using the servo drive's emulated encoder
output, set to $10^5$ counts per turbine shaft revolution. Carriage speed, and
therefore inflow velocity was measured using a linear encoder with 10 $\mu$m
resolution. All of these performance-related quantities were sampled at 2 kHz,
while the tow tank's motion controller provided redundant measurements of the
carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
measurements at 1 meter downstream were measured with a Nortek Vectrino+
acoustic Doppler velocimeter, sampling at 200 Hz. A photo and drawing of the
experimental setup are shown in Fig.~\ref{fig:exp-setup-photo} and
Fig.~\ref{fig:exp-setup}, respectively.

@@

Since the blockage ratio was relatively low (10\%), and a definitive blockage
correction for cross-flow turbines has not been established \cite{Cavagnaro2014}
blockage effects were not corrected for. Furthermore, most numerical modeling
efforts can easily incorporate finite domains, meaning blockage corrections
could create an additional variable to obfuscate validation efforts.
